Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-02-25 paper/paper1/ms.tex
Add the abstract from the ill-fated winter 2021 AAS

\title{Disperse HPF line strengths of exoplanet host stars}

@@

\begin{abstract}
    We measure the line strengths of exoplanet host stars in and out of transit.

\end{abstract}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{stellar_periodogram.png}
    \caption{Periodogram of solely the stellar variation of the flux. }
    \label{fig:stellar_periodogram}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{planetary_periodogram.png}
    \caption{Periodogram of the stellar variation coupled with the planetary transit signal of the flux. }
    \label{fig:planetary_periodogram}
\end{figure}

@@

After collecting the new parameters, we then calculated the equivalent width of the corresponding line with the formula $EW=\sqrt{2\pi}\frac{Aw}{m(\mu-line)+b}$. We then calculated the mean and standard deviation of the equivalent width.
\subsection{Contemporaneous Stellar Activity Quantification}
\subsection{Equivalent Width vs Phase}
\begin{figure}
    \includegraphics[width=\linewidth]{TESS_EW_HAT-P-67.jpg}
    \caption{A boat.}
    \label{fig:boat1}
\end{figure}

>>>>

\title{Atmospheric escape and star-planet-interaction in the HAT-P-67 b system}

@@

\begin{abstract}
    We aim to understand how exoplanet atmospheres evolve across age, stellar irradiation environments, planet properties, and---for extremely close-in exoplanets---direct star-planet interaction (SPI) such as stellar winds, tidal forces, and magnetic interactions. The scarcity of exoplanet atmosphere measurements across a range of stellar properties has limited our ability to complete this picture.

    The Helium Exospheres program with the Habitable Zone Planet Finder (HPF) spectrograph on the Hobby Eberly Telescope (HET) in West Texas has targeted 23 exoplanet systems over two years. Here, we present a study of HAT-P-67, an F subgiant hosting a low density planet with 0.3 $M_{\mathrm{Jup}}$ and 2.1 $R_{\mathrm{Jup}}$ on a close-in 4.8 day orbit. The high energy radiation environment should provide a uniquely harsh testing ground for examining atmospheric escape.  The planet shows prominent in-transit absorption in the He 10830 \AA triplet and infrared Ca II 8542 \AA triplet across 20 visits over the course of a year including in- and out-of-transit spectroscopy. We identify the rotational period of HAT-P-67 to be 5.417 days by using contemporaneous data from the Transiting Exoplanet Survey Satellite (TESS). We consider multiple interpretations of the HPF and TESS observations.  First, the period measured by TESS may be the rotational period of the star and thus, the star and planet are nearly-tidally locked. On the other hand, the period measured by TESS may result from SPI-induced hot spots on the surface that follow the magnetic field lines linked to the planet's orbital period. Finally, we consider the possibility of stellar surface inhomogeneity contaminating the He and Ca II transit signals.
\end{abstract}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/stellar_periodogram.png}
    \caption{Periodogram of solely the stellar variation of the flux. }
    \label{fig:stellar_periodogram}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{figures/planetary_periodogram.png}
    \caption{Periodogram of the stellar variation coupled with the planetary transit signal of the flux. }
    \label{fig:planetary_periodogram}
\end{figure}

@@

After collecting the new parameters, we then calculated the equivalent width of the corresponding line with the formula $EW=\sqrt{2\pi}\frac{Aw}{m(\mu-line)+b}$. We then calculated the mean and standard deviation of the equivalent width.
\subsection{Contemporaneous Stellar Activity Quantification}
\subsection{Equivalent Width vs Phase}
\begin{figure}
    \includegraphics[width=\linewidth]{figures/TESS_EW_HAT-P-67.jpg}
    \caption{A boat.}
    \label{fig:boat1}
\end{figure}
